\textbf{INSERT TITLE HERE}

### 2013-11-16 LaTeX/paper.tex
fixed bug
Added definitions for part 1

\section{Assumptions and Justifications}
\begin{enumerate}
    \item The travel times given are calculated from an optimal route from the center of the first
        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item
        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.

@@

\subsection{Part 1?}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.

>>>>

\section{Assumptions and Justifications}
\begin{enumerate}
    \item The travel times given are calculated from an optimal route from the center of the first
        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item
        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
\end{enumerate}

@@

\subsection{Part 1?}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[A(t) and B(t)] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution.
    \item[v] required ambulance response time
    \item[T_{AB}] travel time from A to B, given
    \item[T_{BA}] travel time from B to A, given
    \item[P_B] total population of B
    \item[T_{A-}] travel time inside of A traveling toward B
    \item[T_{B+}] travel time inside of B traveling away from A
    \item[a and b] width of A and B respectively
    \item[g] width of the gap between A and B
\end{description}
